Dynamic Transition Analysis with TIMES

### 2019-04-24 doc/2019-04-report/2019-04-i2cner-report.tex
updated 2019-04 report
Former-commit-id: 1ae7716de02046a42a2cde65b0f27340c65ed792
Former-commit-id: 61b0be1c8de10aa75e6916b5de3224f77b0c78cc

\subsection{Model details}
The model's assumptions, workings, and the most current list of incorporated technologies is adequately described in the \href{https://github.com/arfc/i2cner/tree/master/doc/2018-09-report}{previous report}, and the I$^2$CNER Energy Analysis Division workshop \href{https://github.com/arfc/i2cner/tree/master/doc/2019-01-poster}{poster} and \href{https://github.com/arfc/i2cner/tree/master/doc/2019-02-presentation}{presentation}.

@@

\item \textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios DSCINV files, whereas the slightly improved semi-discrete capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}. It is desirable that all DSCINV files in the remaining three models include a similar semi-discrete capacity installation structure, as this helps eliminate \href{https://github.com/arfc/i2cner/issues/74}{the production-exceeding-demand bug}.\\

\item \textbf{Incorporation of the contribution-to-peak \cite{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's capacity that is guaranteed to be available during peak demand. This introduces a notion of an energy resource's reliability, thereby introducing a notion of the unreliability of wind and solar. The values in the model \cite{kato_energy_2016} may not be entirely accurate, since they are annually averaged.\\

@@

\item The costs associated with CCS for Japan have been hard to find as Japan, instead of building CCS pipelines like the US or China, intends to build a shipping network for offshore storage of captured and compressed CO$_2$. Based on our interaction with our Energy Analysis Division colleagues at Kyushu university, the costs of this are still being explored by the Japanese government.

@@

\item \textbf{Remove pure oil from all models:} We do not think Japan will ever increase its dependence on oil due to its cost, emissions intensity and due to the Japanese goal of increasing energy independence. Current trends indicate the opposite. While a few models already exclude oil-based energy, other models should also exclude pure oil-based electricity generation for the sake of consistency.

@@

\item \textbf{Revise CCS structure:} Simplified CCS needs to be implemented that emits only 5-10\% of the corresponding fossil fuel. In the model, this should look like any other fossil fuel electricity generation process, except it should be more expensive and have reduced emissions. Such an implementation should \textbf{not} include retrofitting of CCS (i.e. adding carbon capture to previously deployed fossil fuel capacity - discussed below). While we do not have Japan-specific data for CCS, we can simplify our model by using data from the US and:
\begin{itemize}

\item Neglect the difference between Japan and the US, assuming that the government will foot the bill of setting up the CCS shipping network and offshore storage sites.  Japan's shipping network is already well-developed, and further imprmay also tie into Japan's plans to import hydrogen from Australia, steel and fossil fuel from

@@

\item Attempt to conduct a rough ab-initio analysis, by find the cost of offshore-drilling to the depths necessary for CO$_2$ storage, the cost of pressurizing 1 ton of CO$_2$, and the cost of transporting a ton of cargo to offshore storage sites.

@@

\begin{itemize}
\item At the very least demand should increase at +1.7 \% per year until 2030 as per METI projections \cite{noauthor_electricity_2017}, and should plateau afterwards until 2100.

@@

\item Cost Analysis - Some metric to compare the transition costs for each scenario should be calculated. For example, the levelized cost of electricity (LCoE) for each scenario for different years (say 2030,2050,2100) could be calculated, or quite simply the total cost of the transition (investment+generation) could be juxtaposed for each scenario.

@@

\subsection{Stretch Goals}
These targets are neither urgent nor necessary.

>>>>

\subsection{Model details}
The model's assumptions, workings, and the most current list of incorporated technologies is adequately described in the \href{https://github.com/arfc/i2cner/tree/master/doc/2018-09-report}{previous report}, and the 2019 I$^2$CNER Energy Analysis Division workshop \href{https://github.com/arfc/i2cner/tree/master/doc/2019-01-poster}{poster} and \href{https://github.com/arfc/i2cner/tree/master/doc/2019-02-presentation}{presentation}.

@@

\item \textbf{Incorporation of semi-discrete investment sizes:} Discrete investment sizes were incorporated in most scenarios DSCINV files, whereas the slightly improved semi-discrete capacity sizes are incorporated in the \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/co2-constrnt-conv-nonuc}{conventional-no-nuclear model}. It is desired that all DSCINV files in the remaining three models include a similar semi-discrete capacity installation structure, as this helps eliminate \href{https://github.com/arfc/i2cner/issues/74}{the production-exceeding-demand bug}.\\

\item \textbf{Incorporation of the contribution-to-peak \cite{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's capacity that is guaranteed to be available during peak demand. This introduces a notion of an energy resource's reliability, thereby reducing excessive deployment of wind and solar due to their unreliability. The values in the model \cite{kato_energy_2016} may not be entirely accurate, since they are annually averaged.\\

@@

\item We may be overesetimating CCS costs. The costs associated with CCS for Japan have been hard to find as Japan, instead of building CCS pipelines like the US or China, intends to build a shipping network for offshore storage of captured and compressed CO$_2$. Based on our interaction with our Energy Analysis Division colleagues at Kyushu university, the costs of this are still being explored by the Japanese government.

@@

\begin{enumerate}

\item \textbf{Remove pure oil from all models:} We do not think Japan will ever increase its dependence on oil due to its cost, emissions intensity and due to the Japanese goal of increasing energy independence. Current trends support this assumption. While a few models already exclude oil-based energy, other models should also exclude pure oil-based electricity generation for the sake of consistency.

\item \textbf{Incorporate semi-discrete investment sizes:} As stated previously, all DSCINV files must include semi-discrete capacity installation sizes for consistency.

@@

\item \textbf{Revise CCS structure:} Simplified CCS needs to be implemented that emits only 5-10\% of the CO$_2$ that the corresponding fossil fuel technology emits. In the model, this should look like any other fossil fuel electricity generation process, except it should be more expensive and have reduced emissions. Such an implementation should \textbf{not} include retrofitting of CCS (i.e. adding carbon capture to previously deployed fossil fuel capacity - discussed below). While we do not have Japan-specific data for CCS, we can simplify our model by using data from the US and do one of the following:
\begin{itemize}

\item Neglect the difference between Japan and the US, assuming that the government will foot the bill of setting up the CCS shipping network and offshore storage sites.

@@

\item Attempt to conduct a rough ab-initio analysis by finding the cost of offshore-drilling to the depths necessary for CO$_2$ storage, the cost of pressurizing 1 ton of CO$_2$, and the cost of transporting a ton of cargo to offshore storage sites by ship.

@@

\begin{itemize}
\item At the very least, demand should increase at +1.7 \% per year until 2030 as per METI projections \cite{noauthor_electricity_2017}, and should plateau afterwards until 2100.

@@

\item Cost Analysis - Some metric to compare the transition costs for each scenario should be calculated. For example, the levelized cost of electricity (LCoE) for each scenario for different years (say 2030,2050,2100) could be calculated, or the total cost of the transition (investment+generation) could be juxtaposed for each scenario.

@@

\subsection{Stretch Goals}
At this time, these targets are neither urgent nor necessary.
